Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2015-12-07 tex/scam/reviews-v2/response_v2.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand{\baselinestretch}{1.02}

\begin{document}

\vspace*{5pt}

As before, we are grateful to the reviewers for their careful reading
and very helpful editing and suggestions. We have fixed all of the typos
found by the reviewers. We also have improved the paper in other minor
aspects in response to the reviews---these changes are described
below.

@@

\subsection*{Review 4}

\begin{enumerate}
\item \rc{On page 30, I did not understand : ”we set $K = 7$ for all the experiments”, and then ”We set $s = 5$” and ”the true variables are $X_j$ for $j = 5,6,7,8,9,10$”.}

Here, the true function is a soft-max of linear forms $\beta_k^T x$, i.e., 
$$f_0(x) = \log \left( \sum_{k=1}^K \exp( \beta_k^T x) \right) - \mu$$
where the $\beta_k$s are randomly generated unit vectors. $K$ is the
number of linear pieces and $s$ is the number of relevant
variables. We have clarified this a bit more in Section 6 of the
paper.
\end{enumerate}

@@

\item \rc{In Example 3.3, the authors describe a method for approximating any bounded density over a hypercube arbitrarily well using boundary flat densities. The second paragraph mentions truncating the density to the hypercube $[\epsilon, 1−\epsilon]^p$—since the truncated function isn’t a density, it should technically also be rescaled.}

This has been fixed.

\item \rc{In Assumption A4 at the bottom of page 25, the moment generating function should read $\E e^{tW}$ rather than $\E e^{t \epsilon}$. There is some change in notation in Section 6.1, where $W$ is replaced by $\epsilon$; perhaps it would be better to keep the notation consistent.}

We have changed $\epsilon$ to $W$ across the paper to keep the notation consistent.

@@

\item \rc{The last sentence of the first paragraph on page 26 is a bit hard to follow. What does “if $X$ is independent” mean (does this mean $p(x)$ is a product distribution)? I did not understand where the simplification came from.}

``$X$ is independent'' does mean that $p(x)$ is a product distribution; we have clarified this in the paper. We have also added a new section to the supplement (Section 11, Proposition 11.1) that explains and derives the simplification.

\item \rc{The $\nu = 0.9$ curve in Figure 5(d) is rather ill-behaved compared to the other curves. However, if my understanding is correct, the probability of successful screening should still tend to 1 in this case. Perhaps the authors could consider plotting more samples to show eventual consistency for this curve, as well (and also take an average over more trials, since the behavior of the curve is somewhat noisy).}

The probability of successful screening does tend to one. That was not
reflected in the old plot because the old plot describes the
probability both that the number of false positives is zero (successful
screening) and that the number of false positives is less than 20. It
was because of this latter criterion that the $\nu =0.9$ curve did not
tend to one in the old plot. The threshold of 20 was arbitrarily
chosen; we have removed this restriction and revised the plots. The updated figures
5(d) and 5(e) show only the probability that the number of false
negatives is zero; the number of false positives is reflected in the
newly added figures 6(f) and 6(g), which show that total number of
variables selected in the experiments that correspond to figures 5(d)
and 5(e). We have also updated the discussion in Sections 6.1.3 and
6.1.4.

### 2015-12-07 tex/scam/paper-submit.tex
minor
a
new support size plots
response v2
acknowledge
minor edits

\RequirePackage[OT1]{fontenc}
\usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,custom_math,amssymb}
\RequirePackage{hypernat}
\usepackage[ruled,section]{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{graphicx}
\usepackage[hscale=0.7,vscale=0.8]{geometry}
\usepackage{subfigure}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{yhmath}

\renewcommand{\baselinestretch}{1.05}
%\parskip12pt
%\parindent0pt
\setcounter{tocdepth}{2}

@@

\section*{Acknowledgements}
Research supported in part by NSF grants IIS-1116730, 
AFOSR grant FA9550-09-1-0373, ONR grant
N000141210762, and an Amazon AWS in Education Machine Learning
Research grant.

\clearpage
\bibliographystyle{imsart-nameyear}
\bibliography{local}

\clearpage
\input{supplement}

>>>>

\RequirePackage[OT1]{fontenc}
\usepackage{amsthm,amsmath,amsfonts,natbib,mathtools,custom_math,amssymb}
\RequirePackage{hypernat}
\usepackage[ruled,section]{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{graphicx}
%\usepackage[hscale=0.7,vscale=0.8]{geometry}
\usepackage[text={6.0in,8.6in},centering]{geometry}
\usepackage{subfigure}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{yhmath}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{shadecolor}{gray}{0.9}
\definecolor{shadecolor}{gray}{0.9}
\hypersetup{citecolor=MidnightBlue}
\hypersetup{linkcolor=MidnightBlue}
\hypersetup{urlcolor=MidnightBlue}
\usepackage{enumerate}
\usepackage{multirow}

\renewcommand{\baselinestretch}{1.045}
%\parskip12pt
%\parindent0pt
\setcounter{tocdepth}{2}

@@

\section*{Acknowledgements}
Research supported in part by NSF grants IIS-1116730 and DMS-1513594,
AFOSR grant FA9550-09-1-0373, ONR grant N000141210762, and an Amazon
AWS in Education Machine Learning Research grant. The authors 
thank  Ming Yuan for valuable discussions and suggestions
on this research. The authors are also grateful to the anonymous
reviewers whose careful proofreading and helpful comments significantly
improved the quality of the paper.

%\clearpage
\bibliographystyle{imsart-nameyear}
\bibliography{local}

%\clearpage
\input{supplement}

### 2015-12-07 tex/scam/sparsistency.tex
minor edits

Let $\mathcal{C}^1$ denote the set of univariate convex functions
supported on $[-1,1]$, 
and let  $\mathcal{C}_1^{p}$ denote the set of convex additive functions
$\mathcal{C}_1^p \equiv \{ f \,:\, f = \sum_{k=1}^p f_k, \,
   f_k \in \mathcal{C}^1 \} $.  
Let $f^*(\mathbf{x}) = \sum_{k=1}^p f^*_k(x_k)$ be the population risk
minimizer in $\mathcal{C}_1^p$, 
\begin{equation}
f^* = \arg\min_{f \in \mathcal{C}_1^p} \E\big(f_0(X) - f(X)
\big)^2.
\end{equation}
$f^*$ is the unique minimizer by Theorem~\ref{thm:acdc_faithful}. Similarly, we define $\mh \mathcal{C}^1$ as the set of univariate concave functions supported on $[-1, 1]$ and define
\begin{equation}
g^*_k = \arg\min_{g_k \in \mh \mathcal{C}^1} \E \big( f_0(X) - f^*(X)
- g_k(X_k) \big)^2.
\end{equation}
The $\hat{g}_k$s are unique minimizers as well. We let $S = \{ k =
1,\ldots,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$ and let $s =
|S|$. By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it
must be that $S_0 \subset S$ and thus $s \geq s_0$. In some cases,
such as when $X_{S_0}, X_{S^c_0}$ are independent, we have $S = S_0$.
Each of our theorems will use a subset of the following assumptions:
\begin{packed_enum}
\item[A1:] $X_S, X_{S^c}$ are independent. 
\item[A2:] $f_0$ is convex with a bounded second derivative on an open set around $[-1,1]^p$. $\E f_0(X) = 0$.
\item[A3:] $\|f_0\|_\infty \leq sB$ and $\| f^*_k \|_\infty \leq B$ for all $k$.
\item[A4:] $W$ is mean-zero sub-Gaussian, independent of $X$, with scale $\sigma$; i.e., for all $t \in \R$, $\E e^{t W} \leq e^{\sigma^2 t^2 / 2}$.
\item[A5:] The density $p(\mathbf{x})$ satisfies the boundary flatness condition (Definition~\ref{defn:boundary-point}), and $0 < c_l \leq \inf p(\mathbf{x}) \leq \sup p(\mathbf{x}) \leq c_u < \infty$ for two constants $c_l, c_u$. 
\end{packed_enum}
By assumption A1, $f^*_k$ must be zero for $k\notin S$.
We define $\alpha_{+}, \alpha_{-}$ as a measure of the signal strength of the weakest variable:
\begin{align}
\alpha_{+} &= \min_{f \in \mathcal{C}_1^p \,:\, \textrm{supp}(f) \subsetneq \textrm{supp}(f^*)} 
       \Big\{ \mathbb{E} \big( f_0(X) - f(X) \big)^2 - 
        \mathbb{E} \big( f_0(X) - f^*(X) \big)^2  \Big\} \label{eqn:signal_level_defn} \\
\alpha_{-} &=   \min_{k \in S \,:\, g^*_k \neq 0}
      \Big\{ \mathbb{E} \big( f_0(X) - f^*(X) \big)^2 - 
    \mathbb{E} \big( f_0(X) - f^*(X) - g^*_k(X_k) \big)^2 \Big\} \nonumber
\end{align}
The term $\alpha_+$ is a lower bound on the excess risk incurred by
any additive convex function whose support is strictly smaller than
$f^*$. $\alpha_+$ is achieved by some $f \neq f^*$ because the set
$\{f\in \mathcal{C}_1^p\,:\, \trm{supp}(f) \subsetneq
\textrm{supp}(f^*)\}$ is a finite union of closed convex
sets. $\alpha_+ > 0$ since $f^*$ is the unique risk
minimizer. Likewise, $\alpha_-$ lower bounds the excess risk of any
decoupled concave fit of the residual $f_0 - f^*$ that is strictly
more sparse than the optimal decoupled concave fit $\{\hat{g}_k^*\}$;
$\alpha_- > 0$ by the uniqueness of $\{g^*_k\}$ as well. These
quantities play the role of the absolute value of the smallest nonzero
coefficient in the true linear model in lasso theory.  Intuitively, if
$\alpha_{+}$ is small, then it is easier to make a false omission in
the additive convex stage of the procedure. If $\alpha_{-}$ is small,
then it is easier to make a false omission in the decoupled concave
stage of the procedure. If $X$ is independent, then $\alpha_+$ can be
simplified to $\min_{k \,:\, f^*_k \neq 0} \E f^*_k(X)^2$ and
$\alpha_-$ becomes unnecessary (see section~\ref{sec:prod_density_simplification} in the supplementary material).

>>>>

Let $\mathcal{C}^1$ denote the set of univariate convex functions
supported on $[-1,1]$, 
and let  $\mathcal{C}_1^{p}$ denote the set of convex additive functions
$\mathcal{C}_1^p \equiv \{ f \,:\, f = \sum_{k=1}^p f_k, \,
   f_k \in \mathcal{C}^1 \} $.  
Let $f^*(\mathbf{x}) = \sum_{k=1}^p f^*_k(x_k)$ be the population risk
minimizer in $\mathcal{C}_1^p$, 
\begin{equation}
f^* = \arg\min_{f \in \mathcal{C}_1^p} \E\big(f_0(X) - f(X)
\big)^2.
\end{equation}
$f^*$ is the unique minimizer by Theorem~\ref{thm:acdc_faithful}. Similarly, we define $\mh \mathcal{C}^1$ as the set of univariate concave functions supported on $[-1, 1]$ and define
\begin{equation}
g^*_k = \arg\min_{g_k \in \mh \mathcal{C}^1} \E \big( f_0(X) - f^*(X)
- g_k(X_k) \big)^2.
\end{equation}
The $\hat{g}_k$s are unique minimizers as well. We let $S = \{ k =
1,\ldots,p \,:\, f^*_k \neq 0 \trm{ or } g^*_k \neq 0\}$ and let $s =
|S|$. By additive faithfulness (Theorem~\ref{thm:acdc_faithful}), it
must be that $S_0 \subset S$ and thus $s \geq s_0$. In some cases,
such as when $X_{S_0}, X_{S^c_0}$ are independent, we have $S = S_0$.
Each of our theorems will use a subset of the following assumptions:
\begin{packed_enum}
\item[A1:] $X_S, X_{S^c}$ are independent. 
\item[A2:] $f_0$ is convex with a bounded second derivative on an open set around $[-1,1]^p$. $\E f_0(X) = 0$.
\item[A3:] $\|f_0\|_\infty \leq sB$ and $\| f^*_k \|_\infty \leq B$ for all $k$.
\item[A4:] $W$ is mean-zero sub-Gaussian, independent of $X$, with scale $\sigma$; i.e., for all $t \in \R$, $\E e^{t W} \leq e^{\sigma^2 t^2 / 2}$.
\item[A5:] The density $p(\mathbf{x})$ satisfies the boundary flatness condition (Definition~\ref{defn:boundary-point}), and $0 < c_l \leq \inf p(\mathbf{x}) \leq \sup p(\mathbf{x}) \leq c_u < \infty$ for two constants $c_l, c_u$. 
\end{packed_enum}
By assumption A1, $f^*_k$ must be zero for $k\notin S$.
We define $\alpha_{+}, \alpha_{-}$ as a measure of the signal strength of the weakest variable:
\begin{align}
\alpha_{+} &= \min_{f \in \mathcal{C}_1^p \,:\, \textrm{supp}(f) \subsetneq \textrm{supp}(f^*)} 
       \Big\{ \mathbb{E} \big( f_0(X) - f(X) \big)^2 - 
        \mathbb{E} \big( f_0(X) - f^*(X) \big)^2  \Big\} \label{eqn:signal_level_defn} \\
\alpha_{-} &=   \min_{k \in S \,:\, g^*_k \neq 0}
      \Big\{ \mathbb{E} \big( f_0(X) - f^*(X) \big)^2 - 
    \mathbb{E} \big( f_0(X) - f^*(X) - g^*_k(X_k) \big)^2 \Big\} \nonumber
\end{align}
The term $\alpha_+$ is a lower bound on the excess risk incurred by
any additive convex function whose support is strictly smaller than
$f^*$. $\alpha_+$ is achieved by some $f \neq f^*$ because the set
$\{f\in \mathcal{C}_1^p\,:\, \trm{supp}(f) \subsetneq
\textrm{supp}(f^*)\}$ is a finite union of closed convex
sets. $\alpha_+ > 0$ since $f^*$ is the unique risk
minimizer. Likewise, $\alpha_-$ lower bounds the excess risk of any
decoupled concave fit of the residual $f_0 - f^*$ that is strictly
more sparse than the optimal decoupled concave fit $\{\hat{g}_k^*\}$;
$\alpha_- > 0$ by the uniqueness of $\{g^*_k\}$ as well. These
quantities play the role of the absolute value of the smallest nonzero
coefficient in the true linear model in lasso theory.  Intuitively, if
$\alpha_{+}$ is small, then it is easier to make a false omission in
the additive convex stage of the procedure. If $\alpha_{-}$ is small,
then it is easier to make a false omission in the decoupled concave
stage of the procedure. If $p(\mathbf{x})$ is a product density, then $\alpha_+$ can be
simplified to $\min_{k \,:\, f^*_k \neq 0} \E f^*_k(X)^2$ and
$\alpha_-$ becomes unnecessary (see Section~\ref{sec:prod_density_simplification} in the supplementary material).
